Ultrafast manipulation of Heisenberg exchange and Dzyaloshinskii–-Moriya interactions in antiferromagnetic insulators

### 2019-02-12 Paper/paper.tex
add exp values

\begin{figure}[t]
\includegraphics[width=\columnwidth]{../Figures/NNvsNNN.pdf}
\caption{For circularly polarized light we obtain $\tilde{J}_1 = \frac{J_{1,ij}'}{J_{1,ij}}$ and $\tilde{D}_{2} = \frac{D_{2,ij}'}{D_{2,ij}}$ as function of $\mathcal{E} = \frac{eaE_0}{\omega}$, where $e$ is the electron charge and $a$ is the lattice constant. The results are obtain for (units of $\hbar=t_1=1$) $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 4, 14$. Solid lines are for $\omega = 4$ and dashed lines are for $\omega = 14$. For $\tilde{J}_1$, similar results are obtained by Mentink et Al. \cite{Mentink2015}.}
\label{fig2}
\vspace*{-6pt}
\end{figure}
A similar Hamiltonian including a NN exchange term and a NNN DMI term was first proposed by S. A. Owerre to model honeycome topological magnon insulators \cite{Owerre2016} \cite{Elyasi}. Additionally, experimental results regarding topological properties of spin waves in honeycomb ferromagnet Cr$I_3$ can only be understood by considering this Hamiltonian \cite{Chen2018}. This model is also relevant for the study of Spin Hall effects of Weyl magnons \cite{Zyuzin2018} \cite{Sekine2015}.

>>>>

In Figure \ref{fig2} we show the dependence of $J_{1,ij}'$ and $\bs{D}_{2,ij}'$ in the electric parameter $\mathcal{E} = \frac{eaE_0}{\omega}$ where $e$ is the electron charge and $a$ is the lattice constant. The results are obtained for (units of $\hbar=t_1=1$, typically $t \approx 2.8 \text{eV}$ in graphene \cite{CastroNeto2009}) $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ (typical value is $\text{U} \approx 9.3\text{eV}$ in graphene \cite{Wehling2011}) and $\omega = 4, 14$ (equivalently, $T = \frac{2\pi}{\omega} \approx 10^{-16}\text{s}$).

\begin{figure}[t]
\includegraphics[width=\columnwidth]{../Figures/NNvsNNN.pdf}
\caption{For circularly polarized light we obtain $\tilde{J}_1 = \frac{J_{1,ij}'}{J_{1,ij}}$ and $\tilde{D}_{2} = \frac{D_{2,ij}'}{D_{2,ij}}$ as function of $\mathcal{E} = \frac{eaE_0}{\omega}$. Solid lines are for $\omega = 4$ and dashed lines are for $\omega = 14$.}
\label{fig2}
\vspace*{-6pt}
\end{figure}
A similar Hamiltonian including a NN exchange term and a NNN DMI term was first proposed by S. A. Owerre to model honeycome topological magnon insulators \cite{Owerre2016} \cite{Elyasi}. Additionally, experimental results regarding topological properties of spin waves in honeycomb ferromagnet Cr$I_3$ can only be understood by considering this Hamiltonian \cite{Chen2018}. This model is also relevant for the study of Spin Hall effects of Weyl magnons \cite{Zyuzin2018} \cite{Sekine2015}.
